Context-dependent consequences of including lagged effects in demographic models

### 2022-06-15 docs/paper.Rmd
fix relative path issues

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	fig.path = "figures/",
	dev = "png",
	dpi = 300,
	message = FALSE,
	warning = FALSE,
	collapse = TRUE,
	comment = "#>"
)
library(targets)
library(tidyverse)
```

@@

```{r}
meta_df <- 
  tar_meta() %>% 
  select(name, size, bytes, time, seconds) %>% 
  filter(str_detect(name, "^ipm_\\w+_[cf]{2}$")) %>% 
  mutate(minutes = seconds / 60,
         hours = minutes / 60)

@@

tar_read(aic_tbl_df) %>%
  group_by(habitat, model) %>% 
  # mutate(rank = row_number()) %>% 
  ungroup() %>% 
  mutate(habitat = toupper(habitat),
         env_effect_incl = ifelse(
           env_effect_incl != "DLNM",
           to_sentence_case(as.character(env_effect_incl)),
           as.character(env_effect_incl)
         )
  )%>% 
  mutate(
    model = fct_relevel(
      model,
      c("surv", "size", "flwr", "surv_sdlg", "size_sdlg")
    ),
    model = fct_recode(
      model,
      "Survival"          = "surv",
      "Growth"            = "size",
      "Flowering"         = "flwr",
      "Seedling survival" = "surv_sdlg",
      "Seedling growth"   = "size_sdlg"
    )
  ) %>%

@@

```{r lambdas, results='asis'}
tar_read(lambda_table) %>% 
  mutate(habitat = toupper(habitat)) %>% 
  mutate(across(c(est, lower, upper), ~format(round(.,4)))) %>% 
  mutate(lambda = glue::glue("{est} ({lower}, {upper})")) %>%
  mutate(ipm = str_replace_all(
    ipm,
    c(
      "det" = "Deterministic",
      "stoch" = "Stochastic, kernel-resampled",
      "DLNM" = "Stochastic, parameter-resampled"
    )
  )) %>% 
  select(IPM = ipm, Habitat = habitat, "$\\lambda$" = lambda) %>% 
pandoc.table(
  digits = 5,
  keep.trailing.zeros = TRUE,
  justify = c("left", "left", "right"),
  full_width = FALSE,
  caption = "(\\#tab:lambdas) Population growth rates for continuous forest (CF) and forest fragments (FF) under different kinds of IPMs with bootstrapped, bias-corrected, 95% confidence intervals."
)

@@

# Draft of this figure is in docs/figures/Heliconia lifecycle DAG.key
knitr::include_graphics(here::here("docs", "figures", "lifecycle.pdf"))
```

@@

knitr::include_graphics(here::here(tar_read(fig_pop_states)))

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = FALSE,
	fig.path = "figures/",
	dev = "png",
	dpi = 300,
	message = FALSE,
	warning = FALSE,
	collapse = TRUE,
	comment = "#>"
)
library(targets)
library(tidyverse)
library(here)
```

```{r}
#load targets
withr::with_dir(here(), {
  tar_load(c(
    aic_tbl_df,
    lambda_table,
    fig_pop_states
  ))
})
```

@@

```{r}
meta_df <- 
  tar_meta(store = here("_targets")) %>% 
  select(name, size, bytes, time, seconds) %>% 
  filter(str_detect(name, "^ipm_\\w+_[cf]{2}$")) %>% 
  mutate(minutes = seconds / 60,
         hours = minutes / 60)

@@

aic_tbl_df %>%
  group_by(habitat, model) %>% 
  # mutate(rank = row_number()) %>% 
  ungroup() %>% 
  mutate(habitat = toupper(habitat),
         env_effect_incl = ifelse(
           env_effect_incl != "DLNM",
           to_sentence_case(as.character(env_effect_incl)),
           as.character(env_effect_incl)
         )
  )%>% 
  mutate(
    model = fct_relevel(
      model,
      c("surv", "size", "flwr", "surv_sdlg", "size_sdlg")
    ),
    model = fct_recode(
      model,
      "Survival"          = "surv",
      "Growth"            = "size",
      "Flowering"         = "flwr",
      "Seedling survival" = "surv_sdlg",
      "Seedling growth"   = "size_sdlg"
    )
  ) %>%

@@

```{r lambdas, results='asis'}
lambda_table %>% 
  mutate(habitat = toupper(habitat)) %>% 
  mutate(across(c(est, lower, upper), ~format(round(.,4)))) %>% 
  mutate(lambda = glue::glue("{est} ({lower}, {upper})")) %>%
  mutate(ipm = str_replace_all(
    ipm,
    c(
      "det" = "Deterministic",
      "stoch" = "Stochastic, kernel-resampled",
      "DLNM" = "Stochastic, parameter-resampled"
    )
  )) %>% 
  select(IPM = ipm, Habitat = habitat, "$\\lambda$" = lambda) %>% 
pandoc.table(
  digits = 5,
  keep.trailing.zeros = TRUE,
  justify = c("left", "left", "right"),
  full_width = FALSE,
  caption = "(\\#tab:lambdas) Population growth rates for continuous forest (CF) and forest fragments (FF) under different kinds of IPMs with bootstrapped, bias-corrected, 95% confidence intervals."
)

@@

# Draft of this figure is in docs/figures/Heliconia lifecycle DAG.key
path <- here("docs/figures/lifecycle.png")
knitr::include_graphics(path, rel_path = FALSE)
```

@@

knitr::include_graphics(here(fig_pop_states), rel_path = FALSE)
